---
title: "03 Data Wrangling"
date: "2021-04"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```





# US-American Corporations with maximum patents







```{r}
  library(tidyverse)

  # Data Table
  library(data.table)
  
  # Counter
  library(tictoc)
library(vroom)
col_types <- list(
  id = col_character(),
  type = col_character(),
  number = col_character(),
  country = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double()
)

patent_tbl <- vroom(
            file       = "C:/Users/ctaru/Desktop/businessdatascience/Patent_data_reduced/patent.tsv", 
            delim      = "\t", 
            col_types  = col_types,
            na         = c("", "NA", "NULL")
        )

assignee_tbl <- vroom(
            file       = "C:/Users/ctaru/Desktop/businessdatascience/Patent_data_reduced/assignee.tsv", 
            delim      = "\t", 
            col_types  = col_types,
            na         = c("", "NA", "NULL")
        )
patent_assignee <- vroom(
            file       = "C:/Users/ctaru/Desktop/businessdatascience/Patent_data_reduced/patent_assignee.tsv", 
            delim      = "\t", 
            col_types  = col_types,
            na         = c("", "NA", "NULL")
        )
##
  class(patent_tbl)
  
  setDT(patent_tbl)
  
  class(assignee_tbl)

  setDT(assignee_tbl)
    class(patent_assignee )

  setDT(patent_assignee )
  ####importing required info
  
  tic()
  patentandassignee_data <-patent_assignee   %>%
        left_join(assignee_tbl, by = c("assignee_id" = "id")) 
  
  setDT(patentandassignee_data  )
  toc()
  
  ##order the table according to company names .then we know how many repeats are there of the company
patentandassignee_data[,.(organization,patent_id),by=organization]
  filtered_tbl<-     patentandassignee_data[,numberofpatents:=.N,by=organization]#####these are no of entries per organisation .which is the number of patents
   ###find the company with max no of patents

newtab<-filtered_tbl %>%filter(!is.na(organization))%>%select(organization,numberofpatents)%>%group_by(organization) %>%
  slice(n()) %>%
  ungroup() %>%

  arrange(desc(numberofpatents))%>%slice(1:10)
newtab
```

We can see from the table  that  the US company / corporation which has the most patents is the "International Business Machines Corporation" with 7547 patents.

# Maximum patents in the year 2014
```{r}
#question 2 
  library(tidyverse)

  # Data Table
  library(data.table)
  
  # Counter
  library(tictoc)
library(vroom)
col_types <- list(
  id = col_character(),
  type = col_character(),
  number = col_character(),
  country = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double()
)

patent_tbl <- vroom(
            file       = "C:/Users/ctaru/Desktop/businessdatascience/Patent_data_reduced/patent.tsv", 
            delim      = "\t", 
            col_types  = col_types,
            na         = c("", "NA", "NULL")
        )

assignee_tbl <- vroom(
            file       = "C:/Users/ctaru/Desktop/businessdatascience/Patent_data_reduced/assignee.tsv", 
            delim      = "\t", 
            col_types  = col_types,
            na         = c("", "NA", "NULL")
        )
patent_assignee <- vroom(
            file       = "C:/Users/ctaru/Desktop/businessdatascience/Patent_data_reduced/patent_assignee.tsv", 
            delim      = "\t", 
            col_types  = col_types,
            na         = c("", "NA", "NULL")
        )
##
  class(patent_tbl)
  
  setDT(patent_tbl)
  
  class(assignee_tbl)

  setDT(assignee_tbl)
    class(patent_assignee )

  setDT(patent_assignee )
  ####importing required info
  
  tic()
  patentandassignee_data <-patent_assignee   %>%
        left_join(assignee_tbl, by = c("assignee_id" = "id")) 
    ques2_tbl<-patentandassignee_data %>%
        left_join(patent_tbl, by = c("patent_id" = "id"))
  
  setDT(  ques2_tbl  )
  toc()
  ####oder by year and take rows with year 2014
    tic()
ques2_tbl%>% separate(col    =date ,
           into   = c("year", "month","day"),
           sep    = "-")%>%select(organization,year,patent_id)%>%filter(year==2014)%>%group_by(organization)%>%ungroup()%>% arrange(desc(organization))%>%count(organization)%>%arrange(desc(n))%>%filter(!is.na(organization))%>%slice(1:10)

  ######
    
```



We can see from the table once again that even in 2014 the US company / corporation which has the most patents is the "International Business Machines Corporation" with 7547 patents.