---
title: "04 Data Visualization"
date: "2021-04"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.



# Exercise 4 part 1

Last compiled: `r Sys.Date()`
Plotting covid data





```{r}

library(tidyverse)
covid_data_tbl <- read_csv("https://covid.ourworldindata.org/data/owid-covid-data.csv")
new_cov_table<-covid_data_tbl%>%select(continent,date,total_cases)%>%  group_by(continent,date) %>% summarize(total.cases = sum(total_cases)) %>%
    ungroup()


new_cov_table %>% group_by(continent,date)%>% 
    
    ggplot(aes(date,total.cases, fill = continent,color =continent)) +
    
    geom_line(size = 0.5, linetype = 1) +
    # facet_wrap(~ frame_material, ncol = 1) +
  
    theme(legend.position = "bottom")+geom_smooth(method = "loess", span = 0.2)+
  labs(
        title = "Covid cases in the 7 continents",
   
        fill = "continent" ,  
        x = "Date",
        y = "Total cases"

    )

```

The following problem required excess computational power to generate a solution

world <- map_data("world")
covid_data_map<- covid_data_tbl %>%
  select(location,total_deaths, population) %>%group_by(total_deaths,population,location) %>%
    summarise(total_deaths = sum(total_deaths))  %>% ungroup()   %>% group_by(location) %>%
    mutate(pct = total_deaths / population) %>%ungroup() %>%mutate(location = case_when(

    location == "United Kingdom" ~ "UK",
    location == "United States" ~ "USA",
    location == "Democratic Republic of Congo" ~ "Democratic Republic of the Congo",
    TRUE ~ location

  )) %>%rename(region = location)%>%
  distinct()
covid_data_map2<-covid_data_map%>%select(region,total_deaths,population,pct)%>%slice(1:1000)

covid_data_map3 <- left_join(covid_data_map2, world, by = "region")

covid_data_map4<-covid_data_map3%>%slice(1:1000)
ggplot(covid_data_map4 , aes(map_id = region, fill =pct))+
  
  geom_map(map = covid_data_map4,  color = "white")+
  expand_limits(x = covid_data_map4$long, y = covid_data_map4$lat)+
  scale_fill_viridis_c(option = "C")


